Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-19 outputs/paper/paper.Rmd
ggplot

reduced_data %>%
  drop_na(nation_race) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Opinion on National Spending on Improving Conditions of Black Population",
       caption = "Figure 4: Distribution of survey respondents' Race") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

@@

@@

reduced_data %>%
  ggplot(aes(x = nation_welfare, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

>>>>

reduced_data %>%
  drop_na(nation_race) %>%
  drop_na(race) %>%
  ggplot(aes(x = race, fill = nation_race)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Governemnt Spending Enough to Improve Conditions of Black Population?",
       caption = "Figure 4: Opinion on National Spending on Improving Conditions of Black Population") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())

@@

reduced_data %>%
  drop_na(nation_welfare) %>%
  ggplot(aes(x = race, fill = nation_welfare)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Is the US Government Spending Enough on Welfare?",
       caption = "Figure 6: Opinion on National Spending on welfare") +
  facet_wrap(~ pres16) + 
  theme(legend.title = element_blank())
```

``````{r, echo=FALSE}

@@

# reduced_data %>%
#   ggplot(aes(x = nation_welfare, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate")
